\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-04-11 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
renamed free_surface_file to free_or_absorbing_surface_file_zmax for clarity

\item [nodes\_coords\_file] Contains the point locations in Cartesian coordinates of the mesh element corners.
\item [mesh\_file] Contains the mesh element connectivity.
\item [free\_surface\_file] Contains the free surface connectivity. You should put both the surface of acoustic regions and of elastic regions in that file;
that is, list all the element faces that constitute the surface of the model in that file.
\item [absorbing\_surface\_file\_xmax] Contains the surface connectivity of the absorbing boundary surface at the Xmax \\(irrelevant in case of C-PML absorbing conditions).
\item [absorbing\_surface\_file\_xmin] Contains the surface connectivity of the absorbing boundary surface at the Xmin \\(irrelevant in case of C-PML absorbing conditions).
\item [absorbing\_surface\_file\_ymax] Contains the surface connectivity of the absorbing boundary surface at the Ymax \\(irrelevant in case of C-PML absorbing conditions).
\item [absorbing\_surface\_file\_ymin] Contains the surface connectivity of the absorbing boundary surface at the Ymin \\(irrelevant in case of C-PML absorbing conditions).
\item [absorbing\_surface\_file\_bottom] Contains the surface connectivity of the absorbing boundary surface at the bottom \\(irrelevant in case of C-PML absorbing conditions).
\end{description}

@@

This creates several mesh files in directory $\mathtt{CUBIT/MESH/}$:
absorbing\_surface\_file\_{*} (5 files) free\_surface\_file materials\_file
mesh\_file nodes\_coords\_file nummaterial\_velocity\_file

>>>>

\item [nodes\_coords\_file] Contains the point locations in Cartesian coordinates of the mesh element corners.
\item [mesh\_file] Contains the mesh element connectivity. The hexahedral elements can have 8 or 27 nodes.\\
See picture doc/mesh\_numbering\_convention/numbering\_convention\_27\_nodes.jpg to see\\
in which (standard) order the points must be cited. In the case of 8 nodes, just include the first 8 points.
\item [free\_or\_absorbing\_surface\_file\_zmax] Contains the free surface connectivity or \\
the surface connectivity of the absorbing boundary surface at the top (Zmax), \\
depending on whether the top surface is defined as free or absorbing in DATA/Par\_file. \\
You should put both the surface of acoustic regions and of elastic regions in that file;
that is, list all the element faces that constitute the surface of the model in that file.
\item [absorbing\_surface\_file\_xmax] Contains the surface connectivity of the absorbing boundary surface at Xmax \\(also needed in the case of C-PML absorbing conditions,
in order for the code to be able to impose Dirichlet conditions on their outer edge).
\item [absorbing\_surface\_file\_xmin] Contains the surface connectivity of the absorbing boundary surface at Xmin \\(also needed in the case of C-PML absorbing conditions,
in order for the code to be able to impose Dirichlet conditions on their outer edge).
\item [absorbing\_surface\_file\_ymax] Contains the surface connectivity of the absorbing boundary surface at Ymax \\(also needed in the case of C-PML absorbing conditions,
in order for the code to be able to impose Dirichlet conditions on their outer edge).
\item [absorbing\_surface\_file\_ymin] Contains the surface connectivity of the absorbing boundary surface at Ymin \\(also needed in the case of C-PML absorbing conditions,
in order for the code to be able to impose Dirichlet conditions on their outer edge).
\item [absorbing\_surface\_file\_bottom] Contains the surface connectivity of the absorbing boundary surface at the bottom (Zmin) \\(also needed in the case of C-PML absorbing conditions,
in order for the code to be able to impose Dirichlet conditions on their outer edge).
\end{description}

@@

This creates several mesh files in directory $\mathtt{CUBIT/MESH/}$:
absorbing\_surface\_file\_{*} (5 files) free\_or\_absorbing\_surface\_file\_zmax materials\_file
mesh\_file nodes\_coords\_file nummaterial\_velocity\_file
